quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-06 paper-quollr.Rmd
Changed code apperance

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  echo = FALSE, 
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  out.width = "100%")

>>>>

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  echo = FALSE, 
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  comment = ">",
  out.width = "100%")

### 2025-07-06 paper-quollr.tex
Changed code apperance

\begin{verbatim}
#> $scaled_nldr
#> # A tibble: 5,000 x 3
#>     emb1  emb2    ID
#>    <dbl> <dbl> <int>
#>  1 0.707 0.839     1
#>  2 0.231 0.401     2
#>  3 0.232 0.215     3
#>  4 0.790 0.564     4
#>  5 0.761 0.551     5
#>  6 0.445 0.721     6
#>  7 0.900 0.137     7
#>  8 0.247 0.392     8
#>  9 0.325 0.542     9
#> 10 0.278 0.231    10
#> # i 4,990 more rows
#> 
#> $lim1
#> [1] -14.42166  13.32655
#> 
#> $lim2
#> [1] -12.43687  12.32455
\end{verbatim}

@@

\begin{verbatim}
#> $b2
#> [1] 16
#> 
#> $a1
#> [1] 0.08326136
#> 
#> $a2
#> [1] 0.07210645
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 240 x 3
#>        h     c_x     c_y
#>    <int>   <dbl>   <dbl>
#>  1     1 -0.1    -0.0892
#>  2     2 -0.0167 -0.0892
#>  3     3  0.0665 -0.0892
#>  4     4  0.150  -0.0892
#>  5     5  0.233  -0.0892
#>  6     6  0.316  -0.0892
#>  7     7  0.400  -0.0892
#>  8     8  0.483  -0.0892
#>  9     9  0.566  -0.0892
#> 10    10  0.649  -0.0892
#> # i 230 more rows
\end{verbatim}

@@

\begin{verbatim}
#>   hex_poly_id           x           y
#> 1           1 -0.10000000 -0.04116510
#> 2           1 -0.14163068 -0.06520059
#> 3           1 -0.14163068 -0.11327155
#> 4           1 -0.10000000 -0.13730704
#> 5           1 -0.05836932 -0.11327155
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 4
#>    emb1  emb2    ID     h
#>   <dbl> <dbl> <int> <int>
#> 1 0.707 0.839     1   205
#> 2 0.231 0.401     2   109
#> 3 0.232 0.215     3    65
#> 4 0.790 0.564     4   146
#> 5 0.761 0.551     5   146
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 3
#>       h   n_h    w_h
#>   <int> <int>  <dbl>
#> 1    21    12 0.0024
#> 2    22    17 0.0034
#> 3    23    22 0.0044
#> 4    24    10 0.002 
#> 5    25     7 0.0014
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 2
#>       h pts_list  
#>   <int> <list>    
#> 1    21 <int [12]>
#> 2    22 <int [17]>
#> 3    23 <int [22]>
#> 4    24 <int [10]>
#> 5    25 <int [7]>
\end{verbatim}

@@

\begin{verbatim}
#>   h         c_x         c_y n_h w_h
#> 1 1 -0.10000000 -0.08923607   0   0
#> 2 2 -0.01673864 -0.08923607   0   0
#> 3 3  0.06652271 -0.08923607   0   0
#> 4 4  0.14978407 -0.08923607   0   0
#> 5 5  0.23304543 -0.08923607   0   0
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 8
#>    from    to  x_from  y_from    x_to    y_to from_count to_count
#>   <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
#> 1     1     2 -0.1    -0.0892 -0.0167 -0.0892          0        0
#> 2    16    17 -0.0584 -0.0171  0.0249 -0.0171          0        0
#> 3    16    32 -0.0584 -0.0171 -0.0167  0.0550          0        0
#> 4     3    17  0.0665 -0.0892  0.0249 -0.0171          0        0
#> 5    17    18  0.0249 -0.0171  0.108  -0.0171          0        0
\end{verbatim}

@@

\begin{verbatim}
#>   [1]   1   2   3   4   5   6   7   8   9  10  11  12  13  14  15  16  17  18
#>  [19]  19  20  21  22  23  24  25  26  27  28  29  30  31  32  33  34  35  36
#>  [37]  37  38  39  40  41  42  43  44  45  46  47  48  49  50  51  52  53  54
#>  [55]  55  56  57  58  59  60  61  62  63  64  65  66  67  68  69  70  71  72
#>  [73]  73  74  75  76  77  78  79  80  81  82  83  84  85  86  87  88  89  90
#>  [91]  91  92  93  94  95  96  97  98  99 100 101 102 103 104 105 106 107 108
#> [109] 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126
#> [127] 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144
#> [145] 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162
#> [163] 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180
#> [181] 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198
#> [199] 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215 216
#> [217] 217 218 219 220 221 222 223 224 225 226 227 228 229 230 231 232 233 234
#> [235] 235 236 237 238 239 240
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 8
#>       h      x1    x2    x3         x4        x5       x6        x7
#>   <int>   <dbl> <dbl> <dbl>      <dbl>     <dbl>    <dbl>     <dbl>
#> 1    21 -0.992   1.91  1.11 -0.000427   0.000624  0.00749  0.00105 
#> 2    22 -0.906   1.93  1.41 -0.0000183  0.00331  -0.0204  -0.000363
#> 3    23 -0.680   1.93  1.72 -0.000810  -0.00259  -0.00449  0.00153 
#> 4    24 -0.272   1.93  1.96  0.00251    0.00668  -0.0460   0.00128 
#> 5    25  0.0760  1.93  2.00  0.00876    0.00447   0.00851 -0.00195
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 4
#>   pred_emb_1 pred_emb_2    ID pred_hb_id
#>        <dbl>      <dbl> <int>      <int>
#> 1      0.691      0.848     1        205
#> 2      0.191      0.416     2        109
#> 3      0.316      0.199     3         66
#> 4      0.774      0.560     4        146
#> 5      0.774      0.560     5        146
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 1 x 2
#>   Error  RMSE
#>   <dbl> <dbl>
#> 1 1481. 0.180
\end{verbatim}

@@

\begin{verbatim}
#> # A tibble: 5 x 32
#>      ID      x1     x2       x3       x4       x5      x6        x7 pred_hb_id
#>   <int>   <dbl>  <dbl>    <dbl>    <dbl>    <dbl>   <dbl>     <dbl>      <int>
#> 1     1 -0.120  1.64   -1.99     0.0104   0.0125   0.0923 -0.00128         205
#> 2     2 -0.0492 1.51    0.00121 -0.0177   0.00726 -0.0362 -0.00535         109
#> 3     3 -0.774  1.30    0.367   -0.00173  0.0156  -0.0962  0.00335          66
#> 4     4 -0.606  0.246  -1.80    -0.00897 -0.0187  -0.0716  0.00126         146
#> 5     5 -0.478  0.0177 -1.88     0.00848  0.00533  0.0998  0.000677        146
#> # i 23 more variables: model_high_d_x1 <dbl>, model_high_d_x2 <dbl>,
#> #   model_high_d_x3 <dbl>, model_high_d_x4 <dbl>, model_high_d_x5 <dbl>,
#> #   model_high_d_x6 <dbl>, model_high_d_x7 <dbl>, error_square_x1 <dbl>,
#> #   error_square_x2 <dbl>, error_square_x3 <dbl>, error_square_x4 <dbl>,
#> #   error_square_x5 <dbl>, error_square_x6 <dbl>, error_square_x7 <dbl>,
#> #   row_wise_total_error <dbl>, abs_error_x1 <dbl>, abs_error_x2 <dbl>,
#> #   abs_error_x3 <dbl>, abs_error_x4 <dbl>, abs_error_x5 <dbl>, ...
\end{verbatim}

>>>>

\begin{verbatim}
> $scaled_nldr
> # A tibble: 5,000 x 3
>     emb1  emb2    ID
>    <dbl> <dbl> <int>
>  1 0.707 0.839     1
>  2 0.231 0.401     2
>  3 0.232 0.215     3
>  4 0.790 0.564     4
>  5 0.761 0.551     5
>  6 0.445 0.721     6
>  7 0.900 0.137     7
>  8 0.247 0.392     8
>  9 0.325 0.542     9
> 10 0.278 0.231    10
> # i 4,990 more rows
> 
> $lim1
> [1] -14.42166  13.32655
> 
> $lim2
> [1] -12.43687  12.32455
\end{verbatim}

@@

\begin{verbatim}
> $b2
> [1] 16
> 
> $a1
> [1] 0.08326136
> 
> $a2
> [1] 0.07210645
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 240 x 3
>        h     c_x     c_y
>    <int>   <dbl>   <dbl>
>  1     1 -0.1    -0.0892
>  2     2 -0.0167 -0.0892
>  3     3  0.0665 -0.0892
>  4     4  0.150  -0.0892
>  5     5  0.233  -0.0892
>  6     6  0.316  -0.0892
>  7     7  0.400  -0.0892
>  8     8  0.483  -0.0892
>  9     9  0.566  -0.0892
> 10    10  0.649  -0.0892
> # i 230 more rows
\end{verbatim}

@@

\begin{verbatim}
>   hex_poly_id           x           y
> 1           1 -0.10000000 -0.04116510
> 2           1 -0.14163068 -0.06520059
> 3           1 -0.14163068 -0.11327155
> 4           1 -0.10000000 -0.13730704
> 5           1 -0.05836932 -0.11327155
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>    emb1  emb2    ID     h
>   <dbl> <dbl> <int> <int>
> 1 0.707 0.839     1   205
> 2 0.231 0.401     2   109
> 3 0.232 0.215     3    65
> 4 0.790 0.564     4   146
> 5 0.761 0.551     5   146
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 3
>       h   n_h    w_h
>   <int> <int>  <dbl>
> 1    21    12 0.0024
> 2    22    17 0.0034
> 3    23    22 0.0044
> 4    24    10 0.002 
> 5    25     7 0.0014
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 2
>       h pts_list  
>   <int> <list>    
> 1    21 <int [12]>
> 2    22 <int [17]>
> 3    23 <int [22]>
> 4    24 <int [10]>
> 5    25 <int [7]>
\end{verbatim}

@@

\begin{verbatim}
>   h         c_x         c_y n_h w_h
> 1 1 -0.10000000 -0.08923607   0   0
> 2 2 -0.01673864 -0.08923607   0   0
> 3 3  0.06652271 -0.08923607   0   0
> 4 4  0.14978407 -0.08923607   0   0
> 5 5  0.23304543 -0.08923607   0   0
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>    from    to  x_from  y_from    x_to    y_to from_count to_count
>   <int> <int>   <dbl>   <dbl>   <dbl>   <dbl>      <dbl>    <dbl>
> 1     1     2 -0.1    -0.0892 -0.0167 -0.0892          0        0
> 2    16    17 -0.0584 -0.0171  0.0249 -0.0171          0        0
> 3    16    32 -0.0584 -0.0171 -0.0167  0.0550          0        0
> 4     3    17  0.0665 -0.0892  0.0249 -0.0171          0        0
> 5    17    18  0.0249 -0.0171  0.108  -0.0171          0        0
\end{verbatim}

@@

\begin{verbatim}
>   [1]   1   2   3   4   5   6   7   8   9  10  11  12  13  14  15  16  17  18
>  [19]  19  20  21  22  23  24  25  26  27  28  29  30  31  32  33  34  35  36
>  [37]  37  38  39  40  41  42  43  44  45  46  47  48  49  50  51  52  53  54
>  [55]  55  56  57  58  59  60  61  62  63  64  65  66  67  68  69  70  71  72
>  [73]  73  74  75  76  77  78  79  80  81  82  83  84  85  86  87  88  89  90
>  [91]  91  92  93  94  95  96  97  98  99 100 101 102 103 104 105 106 107 108
> [109] 109 110 111 112 113 114 115 116 117 118 119 120 121 122 123 124 125 126
> [127] 127 128 129 130 131 132 133 134 135 136 137 138 139 140 141 142 143 144
> [145] 145 146 147 148 149 150 151 152 153 154 155 156 157 158 159 160 161 162
> [163] 163 164 165 166 167 168 169 170 171 172 173 174 175 176 177 178 179 180
> [181] 181 182 183 184 185 186 187 188 189 190 191 192 193 194 195 196 197 198
> [199] 199 200 201 202 203 204 205 206 207 208 209 210 211 212 213 214 215 216
> [217] 217 218 219 220 221 222 223 224 225 226 227 228 229 230 231 232 233 234
> [235] 235 236 237 238 239 240
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 8
>       h      x1    x2    x3         x4        x5       x6        x7
>   <int>   <dbl> <dbl> <dbl>      <dbl>     <dbl>    <dbl>     <dbl>
> 1    21 -0.992   1.91  1.11 -0.000427   0.000624  0.00749  0.00105 
> 2    22 -0.906   1.93  1.41 -0.0000183  0.00331  -0.0204  -0.000363
> 3    23 -0.680   1.93  1.72 -0.000810  -0.00259  -0.00449  0.00153 
> 4    24 -0.272   1.93  1.96  0.00251    0.00668  -0.0460   0.00128 
> 5    25  0.0760  1.93  2.00  0.00876    0.00447   0.00851 -0.00195
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_hb_id
>        <dbl>      <dbl> <int>      <int>
> 1      0.691      0.848     1        205
> 2      0.191      0.416     2        109
> 3      0.316      0.199     3         66
> 4      0.774      0.560     4        146
> 5      0.774      0.560     5        146
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 1 x 2
>   Error  RMSE
>   <dbl> <dbl>
> 1 1481. 0.180
\end{verbatim}

@@

\begin{verbatim}
> # A tibble: 5 x 32
>      ID      x1     x2       x3       x4       x5      x6        x7 pred_hb_id
>   <int>   <dbl>  <dbl>    <dbl>    <dbl>    <dbl>   <dbl>     <dbl>      <int>
> 1     1 -0.120  1.64   -1.99     0.0104   0.0125   0.0923 -0.00128         205
> 2     2 -0.0492 1.51    0.00121 -0.0177   0.00726 -0.0362 -0.00535         109
> 3     3 -0.774  1.30    0.367   -0.00173  0.0156  -0.0962  0.00335          66
> 4     4 -0.606  0.246  -1.80    -0.00897 -0.0187  -0.0716  0.00126         146
> 5     5 -0.478  0.0177 -1.88     0.00848  0.00533  0.0998  0.000677        146
> # i 23 more variables: model_high_d_x1 <dbl>, model_high_d_x2 <dbl>,
> #   model_high_d_x3 <dbl>, model_high_d_x4 <dbl>, model_high_d_x5 <dbl>,
> #   model_high_d_x6 <dbl>, model_high_d_x7 <dbl>, error_square_x1 <dbl>,
> #   error_square_x2 <dbl>, error_square_x3 <dbl>, error_square_x4 <dbl>,
> #   error_square_x5 <dbl>, error_square_x6 <dbl>, error_square_x7 <dbl>,
> #   row_wise_total_error <dbl>, abs_error_x1 <dbl>, abs_error_x2 <dbl>,
> #   abs_error_x3 <dbl>, abs_error_x4 <dbl>, abs_error_x5 <dbl>, ...
\end{verbatim}
